\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-06-21 AffineLieAlgebras/InformalNotes/article.tex
Article is almost finished.

\newtheorem{statement}{Statement}
\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\go}{\overset{\circ }{\frak{g}}}
\newcommand{\ao}{\overset{\circ }{\frak{a}}}
\newcommand{\co}[1]{\overset{\circ }{#1}}

@@

We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations.

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the notations used throughout the paper. In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules of algebra $\mathfrak{g}$ with respect to a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}). In the Section \ref{sec:examples} we present several examples and discuss some applications in CFT models (Section \ref{sec:phys-appl}). We conclude the paper with a review of obtained results. Possible future developments are discussed (Section \ref{sec:conclusion}).

@@

\noindent $=\left\{
\begin{array}{c}
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\text{ }\left( \text{resp. }%
\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \frak{a}\right) i}^{\vee }\right)
\text{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\text{ }\left( \text{resp. }\sum_{i=1}^{r}%
\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \text{for }A_{r}^{\left(
u\geq 2\right) }\text{ and }A\neq A_{2r}^{\left( 2\right) },
\end{array}
\right\} ;$
$\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ --- the corresponding singular weight
element for the $\frak{a}$-module $L_{\frak{a}}^{\nu }$;

@@

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then
the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and
it is clear that $\Delta^{+}_{\bot}$ is empty.
On the other hand
non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
through the chain of maximal embeddings
$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
The maximal regular embeddings are constructed by the exclusion of one or two roots
from the extended Dynkin diagram of the algebra. Since this process can give us
non-connected Dynkin diagrams we can see which roots are orthogonal to the root
space of non-maximal regular subalgebra $\mathfrak{a}$.

Consider for instance the regular embedding of $A_1\subset B_2$.
The extended Dynkin diagram of $B_2$ is presented in the Figure \ref{fig:B2Dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=50mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
Drop the central node to describe the embedding $A_1\oplus A_1\subset B_2$.
In this case we have: $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

@@

The task of the construction of non-diagonal modular invariants is not easy. 
Consider the Wess-Zumino-Witten model with the affine Lie algebra $\mathfrak{a}$. Non-diagonal modular invariants for this model can be constructed from the diagonal invariant if there exists affine algebra $\mathfrak{g}$ such that $\mathfrak{a}\subset\mathfrak{g}$. 
Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function (\ref{eq:36})
by the decompositions
\begin{equation}
  \label{eq:32}
\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}  
\end{equation}
containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules. Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
\begin{equation}
  \label{eq:36}
   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
\end{equation}
The reduction of the representations is crucial in this construction.

@@

The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used to prove the finite reducibility theorem \cite{kac1988modular}. It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
\begin{comment}
  There exists a classification of modular invariant partition functions for some cases, see . [116, 219, 117, 119, 46] in \cite{Fuchs:2009iz}.
\end{comment}
\begin{comment}
  Formulate this as lemma

It is important to note that the orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$. It can be seen from the following consideration. In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
The energy-momentum tensor can be expanded into the modes $L_n$
\begin{equation}
\label{eq:47}
  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
\end{equation}
The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
\begin{equation}
\label{eq:48}
  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
\end{equation}
The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$. But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
\end{comment}

\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
\label{sec:spec-embedd-hata_1s}
Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $A_1\subset A_2$ with the embedding index $x_e=4$. The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.

@@

@@

The set $\widehat{\Psi^{(\omega_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade. We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.

@@

Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}). 
Here we restricted the calculations to the first eight grades.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
  \caption{The fan $\Gamma_{\hat{A_1}\subset \hat{A_2}}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

@@

We are interested in the reduction of the fundamental modules of $\hat A_3$.
Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     \omega_0 & = & (0,0,0,0;1;0),\\
     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
  \end{array}
\end{equation}

@@

The set $\Delta^{+}_{\bot}$ is empty. 
The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}. Coordinates of fan element's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$. Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
\begin{figure}[h!tb]
  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
  \label{fig:A1+A1-A3_fan}
\end{figure}

We limit our calculations by the first 5 grades.
\begin{figure}[h!tb]
  \hspace*{-1cm}
  \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
  \caption{Projected anomalous weights for $L^{\omega_2}_{\hat A_3}$}
  \label{fig:A1+A1-A3_anom}
\end{figure}

The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{\omega_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,1,0;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}. Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$. The weights are shown by crosses if the determinant has the value $\epsilon(\omega)=1$ and by diamonds otherwise.

The diagrams for  $L^{\omega_0}_{\hat A_3}, L^{\omega_1}_{\hat A_3}, L^{\omega_1}_{\hat A_3}$ are similar to that of $L^{\omega_2}_{\hat A_3}$.

The anomalous branching coefficients for the module $L^{(\omega_2)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
\begin{figure}[h!tb]
%  \hspace*{-1cm}
  \includegraphics[width=135mm]{A1+A1-A3_branching.pdf}
  \caption{Anomalous branching coefficients for $L^{(0,1,0;1;0)}_{\hat A_3}$}
  \label{fig:A1+A1-A3_branching}
\end{figure}

@@

Another natural setting where the reduction problem for affine Lie algebras appears is the coset construction of rational conformal field theories \cite{Goddard198588}. Coset models are tightly connected with the gauged WZW-models and are actively studied in string theory especially in string models on anti-de-Sitter space \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}. The characters of the coset model are connected with the branching functions in the following way:
\begin{equation}
  \label{eq:31}
  \chi
\end{equation}
The problem of the branching functions construction in coset models was considered in the papers \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}. The results were mostly given in rather cumbersome form and could not be easily used in computations. The method of calculation of the branching coefficients proposed in this text can be used to get power series expansion of the branching functions up to any required degree. In future work we are going to write complete expansion of the branching functions.

@@

Using the definition (\ref{fan-defined}) we get the fan $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
Here we restricted the computation to the twelfth grade.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=135mm]{AffineB2_A1_fan.pdf}
  \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

The set of the anomalous weights for this module up to the sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade its form is similar to that in the  Figure \ref{fig:B2_A1}.

\begin{figure}[h!tb]
  \hspace*{-2cm}
  \includegraphics[width=200mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$}.
  \label{fig:affine_B2_anom_point}
\end{figure}

@@

Selecting the elements inside the  Weyl chamber
$\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
we get the following results for the branching coefficients up to twelfth grade
\begin{multline}
  \label{eq:28}
  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
    1180 L_{\hat{A_1}}^{w_0}(-12)
\end{multline}
This result can be presented as the set of branching functions \cite{kac1990idl}.
\begin{eqnarray}
  \label{eq:29}
  \begin{array}{cc}
    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray}
Here the lower index enumerates the branching function according to their highest weights in $P^+_{\hat{A_1}}$, these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.

This expansion can be used to compute the conformal dimensions of the primary fields of $B_2/A_1$ coset model in the following way:
\begin{equation}
  \label{eq:35}
  \Delta_{\mu}=
\end{equation}

>>>>

\newtheorem{statement}{Statement}
\newtheorem{note}{Note}[section]
\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\go}{\overset{\circ }{\frak{g}}}
\newcommand{\ao}{\overset{\circ }{\frak{a}}}
\newcommand{\co}[1]{\overset{\circ }{#1}}

@@

We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations. In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of the characters and states.

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the notations used throughout the paper. In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules of algebra $\mathfrak{g}$ with respect to a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several simple examples for finite-dimensional Lie algebras to illustrate the algorithm. Then we consider the affine Lie algebras with the applications in CFT models (Section \ref{sec:phys-appl}). We conclude the paper with a review of obtained results. Possible future developments are discussed (Section \ref{sec:conclusion}).

@@

\noindent $=\left\{
\begin{array}{c}
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\text{ }\left( \text{resp. }%
\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \frak{a}\right) i}^{\vee }\right)
\text{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\text{ }\left( \text{resp. }\sum_{i=1}^{r}%
\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \text{for }A_{r}^{\left(
u\geq 2\right) }\text{ and }A\neq A_{2r}^{\left( 2\right) },
\end{array}
\right\} ;$\\
$\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ --- the corresponding singular weight
element for the $\frak{a}$-module $L_{\frak{a}}^{\nu }$;

@@

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then
the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and
it is clear that $\Delta^{+}_{\bot}$ is empty.
On the other hand
non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
through the chain of maximal embeddings
$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
The maximal regular embeddings are constructed by the exclusion of one or two roots
from the extended Dynkin diagram of the algebra. Since this process can give us
non-connected Dynkin diagrams we can see which roots are orthogonal to the root
space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras of affine Lie algebras can be found in the recent paper \cite{JPhysA2008}.

Consider for instance the regular embedding of $A_1\subset B_2$.
The extended Dynkin diagram of $B_2$ is presented in the Figure \ref{fig:B2Dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
Drop the central node to describe the embedding $A_1\oplus A_1\subset B_2$.
In this case we have: $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

@@

The task of the construction of non-diagonal modular invariants is not easy, although the complete classification of modular invariants for some models is known [116, 219, 117, 119, 46] in \cite{Fuchs:2009iz}.

Consider the Wess-Zumino-Witten model with the affine Lie algebra $\mathfrak{a}$. Non-diagonal modular invariants for this model can be constructed from the diagonal invariant if there exists affine algebra $\mathfrak{g}$ such that $\mathfrak{a}\subset\mathfrak{g}$. 
Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function (\ref{eq:36})
by the decompositions
\begin{equation}
  \label{eq:32}
\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}  
\end{equation}
containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules. Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
\begin{equation}
  \label{eq:36}
   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
\end{equation}
The reduction of the representations is crucial in this construction.

@@

The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used to prove the finite reducibility theorem \cite{kac1988modular}. It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.

\begin{note} The orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
\begin{proof} It can be seen from the following consideration. In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
The energy-momentum tensor can be expanded into the modes $L_n$
\begin{equation}
\label{eq:47}
  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
\end{equation}
The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
\begin{equation}
\label{eq:48}
  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
\end{equation}
The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$. But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
\end{proof}
\end{note}
\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
\label{sec:spec-embedd-hata_1s}
Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $A_1\subset A_2$ with the embedding index $x_e=4$. The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.

@@

Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).

\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{AffineA2_A1_fan.pdf}
  \caption{The fan for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

@@

The set $\widehat{\Psi^{(w_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade. The weights $\omega (w_0+\rho)-\rho$ is shown as cross if $\epsilon(\omega)=1$ and by diamond if $\epsilon(\omega)=-1$. Simple roots of classical subalgebra $A_2$ are shown in grey and grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.

@@

@@

We are interested in the reduction of the fundamental modules of $\hat A_3$.
Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     w_0 & = & (0,0,0,0;1;0),\\
     w_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
     w_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
     w_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
  \end{array}
\end{equation}

@@

The set $\Delta^{+}_{\bot}$ is empty. 
The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}. Coordinates of fan element's finite part are given in the basis of fundamental roots of $A_1\oplus A_1$. Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
\begin{figure}[h!tb]
  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
  \label{fig:A1+A1-A3_fan}
\end{figure}

We limit our calculations by the first 5 grades.
%\begin{figure}[h!tb]
\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm]{A1+A1-A3_anom.pdf}
  \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3}$}
  \label{fig:A1+A1-A3_anom}
\end{figure}

The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{w_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=w_2=(0,1,0;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}. Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$. The weights are shown by crosses if the determinant has the value $\epsilon(\omega)=1$ and by diamonds otherwise.

The diagrams for  $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_1}_{\hat A_3}$ are similar to that of $L^{w_2}_{\hat A_3}$.

The anomalous branching coefficients for the module $L^{(w_2)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}. The anomalous branching coefficients in the $C_{\frak{a}}$ are equal to the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$ and are shown by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
%\begin{figure}[h!tb]
\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.pdf}
  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3}$}
  \label{fig:A1+A1-A3_branching}
\end{figure}

@@

Another natural setting where the reduction problem for affine Lie algebras appears is the coset construction of rational conformal field theories \cite{Goddard198588}. Coset models are tightly connected with the gauged WZW-models and are actively studied in string theory especially in string models on anti-de-Sitter space \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}. The characters of the coset model are connected with the branching functions in the following way:
\begin{equation}
  \label{eq:31}
  \chi^{(\mu)}_{\nu}(\tau)=e^{2\pi i \tau (m_{\mu}-m_{\nu})} b^{(\mu)}_{\nu}(\tau),
\end{equation}
where
\begin{equation}
  \label{eq:46}
  m_{\mu}=\frac{\left|\mu+\rho\right|^2}{2(k+g)}-\frac{\left|\rho\right|^2}{2g}.
\end{equation}

The problem of the branching functions construction in the coset models was considered in the papers \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}. The results were mostly given in rather cumbersome form and could not be easily used in computations. The method of calculation of the branching coefficients proposed in this text can be used to get power series expansion of the branching functions up to any required degree. In future work we are going to write complete expansion of the branching functions.

@@

Using the definition (\ref{fan-defined}) we get the fan $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
Here we restricted the computation to the twelfth grade.
\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{AffineB2_A1_fan.pdf}
  \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

The set of the anomalous weights for this module up to the sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point}. In the grade 0 it is exactly the set of the anomalous weights for the embedding of the classical Lie algebras $A_1\subset B_2$ depicted in the  Figure \ref{fig:B2_A1}. The weights $\omega (w_1+\rho)-\rho$ is shown as cross if $\epsilon(\omega)=1$ and by circle otherwise. Simple roots of classical subalgebra $B_2$ are shown in grey and grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$. The weights of the grade 0 are depicted at the Figure \ref{fig:B2_A1}}.
  \label{fig:affine_B2_anom_point}
\end{figure}

@@

Selecting the elements inside the  Weyl chamber
$\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
we get the following results for the branching coefficients up to twelfth grade
\begin{multline}
  \label{eq:28}
  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
    1180 L_{\hat{A_1}}^{w_0}(-12)
\end{multline}
This result can be presented as the set of branching functions \cite{kac1990idl}.
\begin{eqnarray}
  \label{eq:29}
  \begin{array}{cc}
    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray}
Here the lower index enumerates the branching function according to their highest weights in $P^+_{\hat{A_1}}$, these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$, and $q=\exp (2\pi i \tau)$.
